\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-04-07 abstract.tex
.

Sampling based falsification techniques for black box hybrid dynamical
systems use numerical simulations to search for violations of
properties (specified in temporal logic). This constraints them to a
`best effort' category unlike rigorous verification techniques, which
however require a white box model. This work tries to bridge the gap
by presenting an automatic falsification technique which models the
black box system before searching for a violation. It proceeds by (a)
modeling the behavior of the system using a piecewise affine (PWA)
discrete time model and, (b) encoding the search for a violation as a
standard bounded model checking problem. The resulting problem is a
disjunction of linear programs and can be solved directly using
off-the-shelf SMT solvers or by multiple runs of a linear programming
solver. If a counter-example is found, the existence of a
corresponding violation in the original system is checked for
reproducibility.

>>>>

% Sampling based falsification techniques for black box hybrid dynamical
% systems use numerical simulations to search for violations of
% properties (specified in temporal logic). This constraints them to a
% `best effort' category unlike rigorous verification techniques, which
% however require a white box model. This work tries to bridge the gap
% by presenting an automatic falsification technique which models the
% black box system before searching for a violation. It proceeds by (a)
% modeling the behavior of the system using a piecewise affine (PWA)
% discrete time model and, (b) encoding the search for a violation as a
% standard bounded model checking problem. The resulting problem is a
% disjunction of linear programs and can be solved directly using
% off-the-shelf SMT solvers or by multiple runs of a linear programming
% solver. If a counter-example is found, the existence of a
% corresponding violation in the original system is checked for
% reproducibility.

Models of embedded control systems are often so complex that they can
be treated as effectively black-box systems. Sampling-based methods
for testing such systems use numerical simulations to search for
violations of properties (specified in a suitable requirement
formalism, such as temporal logic). This constrains them to a `best
effort' category unlike rigorous verification techniques, which
however require a model amenable to symbolic analysis. This work tries
to bridge the gap by presenting an automatic falsification technique
which learns a data-driven abstraction of the black box system before
searching for a violation. It proceeds by (a) modeling the behavior of
the system using a piecewise affine (PWA) discrete-time {\em
relational} model and, (b) encoding the search for a violation in the
abstract model as a bounded model checking problem. The bounded model
checking query in this instance can be viewed as a disjunction of
conjunctions of linear constraints (i.e. linear programs) and can be
solved directly using off-the-shelf SMT solvers or by multiple runs of
a linear programming solver. For any counter-example found in the
abstraction, we check the existence of a corresponding violation in
the original system. We demonstrate the efficacy of our technique on a
few dynamical systems examples.

### 2017-04-07 implementation.tex
.

\begin{table}[!htbp]
\centering
\caption{Avg. timings for benchmarks. The \textbf{BMC} column lists
time taken by the BMC engine. The total time in seconds (rounded off
to an integer) is noted under \textbf{S3CAM-R} and \textbf{S3CAM}.
$TO$ signifies time $>5hr$, after which the search was killed.}
\label{tab:res-rel}
\begin{tabular}{@{}llll@{}}
\toprule
Benchmark & BMC & S3CAM-R & S3CAM\\
\midrule
Van der Pol ($\prop_3$)   &$<$1 & $130$ & $24$\\
Brusselator               &$<$1  & $4$    & $2$\\
Lorenz                    &$<$1 & $122$  & $35$\\
%B.Ball                    &  &   & \\
Nav ($\prop_P$)           &$4480$ &$9423$   &$603$ \\
Nav ($\prop_Q$)           &$970$  &$8105$   &$546$ \\
Nav ($\prop_R$)           &-  &$TO$   & $2003$\\
Nav ($\prop_S$)           &-  &$TO$   & $2100$\\
Bouncing Ball             &-  &$TO$   & $450$\\

>>>>

\begin{table}[!htbp]
\centering
\caption{Avg. timings for benchmarks. The \textbf{BMC} column lists
time taken by the BMC engine. The total time in seconds (rounded off
to an integer) is noted under \textbf{S3CAM-R} and \textbf{S3CAM}.
$TO$ signifies time $>5hr$, after which the search was killed.}
\label{tab:res-rel}
\begin{tabular}{@{}llll@{}}
\toprule
    Benchmark & PWA Rel + BMC & PWA Rel + LP & S3CAM\\
\midrule
    Van der Pol ($\prop_3$)   &$130$ & $0$ & $24$\\
    Brusselator               &$4$ & $0$ & $2$\\
    Lorenz                    &$122$ & $0$ & $35$\\
%B.Ball                    &  &   & \\
    Nav ($\prop_P$)           &$TO$ & $2100$  & $603$ \\%9423 + 4480
    Nav ($\prop_Q$)           &$TO$ & $25m$   & $546$ \\%8105 + 970
    Nav ($\prop_R$)           &$TO$ & $0$  & $2003$\\
    Nav ($\prop_S$)           &$TO$ & $0$  & $2100$\\
    Bouncing Ball             &$TO$ & $0$  & $450$\\

### 2017-04-07 prelims.tex
.

In this section, we present the model of the hybrid dynamical system
under test and the basics of pwa relational abstraction.

We now use the family of reachability relations presented
in~\cite{zutshi2014multiple} to charecterize the system $\System$
under test. We denote the states of the hybrid system $\System$, by $\HybridStates \subseteq \Modes \times \Reals^n$ be the (infinite)
set of hybrid states of the system $\System$, where $\Modes$ is a
finite set of discrete modes, and $\Inputs$ be the set of input
signals to $\System$ of the form $[0,T] \rightarrow \reals^k$ for some
given time horizon $T$. The family of
relations $\reach{t,u} \subseteq \HybridStates \times \HybridStates$,
parameterized by time $t \geq 0$ and input signal $u \in \Inputs$
defined over time $[0,T]$.  We use the notation $\vx\ \reach{t,u} \vy$
to denote $(\vx,\vy) \in \reach{t,u}$. The relations $\reach{t,u}$
satisfy the following basic properties:

We assume a black-box model
equipped with a forward simulation map $\simulate^{\System}$ that can
be used to compute the discrete time traces of the system. Let
$\reach{}$ Given the
hybrid state space $\vx\in\HybridStates$ and input space $u
\in\Inputs$ and time step $\Delta_t$, it computes the unique successor
state $\vy=\simulate^{\System}(\vx,u,t)$ such that $\vx \reach{t,u}
\vy$.

\begin{definition}

    The system under test $\System$ evolves in the set of infinite
    hybrid state-space $\HybridStates$ under the effect of inputs $\vu
    \in \Inputs$. Its evolution is defined by a simulation function
    $\simulate^\System : \HybridStates \times \Inputs \Reals^+ \mapsto
    \HybridStates$, where $\simulate^\System(\x,\vu,\Delta_t)$ maps a
    current state $\x$ at time $t$ to a new state $\x'$ at time
    $t+\Delta_t$, under a constant input $\vu$.

The subscript $\System$ will be dropped whenever the system $\System$
being referred to is clear from the context.

\myipara{Black-Box Assumptions:} For above properties of the
$\reach{t,u}$ relation to hold, we require that $\System$ be
deterministic. We also assume that $\System$ can be simulated from a
given initial state using function $\simulate^{\System}$. This
requires existence and uniqueness of trajectories over a finite time
horizon $[0,T]$, which can be guaranteed by Lipschitz continuity of
the vector field in each hybrid mode and ruling away issues such as
finite escape times~\cite{Meiss/2007/Differential}. From a practical
standpoint, these assumptions do not pose significant restrictions for
the type of problems that we wish to address.  Finally, we assume full
observability of the system state, ignore numerical errors due to
simulation and {\em do not} assume that an analytic closed-form
representation of the system dynamics is available.

@@

@@

The
Let the data set be comprised of $N$ input and output pairs $(\x, y)$,
where $\x\in\reals^n$ and $y\in\reals$. If $N>n$, which is the case in
the current context of \textit{finding the best fit}, the problem is
over-determined; there are more equations than unknowns. Hence, a
single affine function cannot be found which satisfies the equation
$\forall i\in\{1\ldots N\}. y_i = \vec{a}^T\x_i + b$. Instead, we need
to find the `best' choice for $\vec{a}$ and $b$. This is formally
defined using a loss function. For the case of simple linear
regression or OLS, the loss function is the sum of squares of the
errors in prediction.  The task is then to determine the vector of
coefficients $\vec{a}$ and an offset constant $b$, such that the least
square error of the affine predictor is minimized for the given data
set.
\begin{equation}
    \operatornamewithlimits{argmin}_{\vec{a}, b}\displaystyle\sum_{i=1}^{N}{\left(\y_i - (\vec{a}^T\x_i + b)\right)^2}
\label{reg}
\end{equation}
To ease the presentation, we can rewrite the above as a homogeneous
expression by augmenting $\x$ by $\hat{\x} = \begin{bmatrix}\x \\ 1\end{bmatrix}$ and replacing $\vec{a}$ and $b$ by the vector
$\vec{ab} = \begin{bmatrix}\vec{a} \\ b \end{bmatrix}$. The equation~\ref{reg} now becomes
\[
    \operatornamewithlimits{argmin}_{\vec{ab}}\displaystyle\sum_{i=1}^{N}{(\y_i - \vec{ab}^T \hat{\x}_i)^2}
\]
The solution of OLS can be analytically computed as
\[ Ab = (X^TX)^{-1}X^T\y\]
where $X$ is the matrix representing the horizontal stacking of all
$\hat{\x}$.
The details can be found in several texts on learning and statistics
\cite{friedman2001elements}.

@@

\subsection{Relational Abstractions}
For a hybrid automaton model, they can summarize the continuous
dynamics of each mode using a binary relation over continuous states.
The resulting relations are timeless (independent) and hence valid for
all time as long as the mode invariant is satisfied. The relations
take the general form of $R(\x,\x') \bowtie 0$, where $\bowtie$
represents one of the relational operators $=, \ge, \le, <, >$. For
example, an abstraction that captures the monotonicity with respect to
time for the differential equation $\dot{x} = 2$ is $x' > x$. The
abstraction capturing the relation between the set of ODEs: $\dot{x} =
2$, $\dot{y} = 5$, is $5(x' - x) = 2(y' - y)$.

@@

We define the PWA transition system as a transition system
%(ref.~\secref{DiscSys})
$\rho:\tupleof{\pLocs,\pVars,\scrT, \pLocI,\Theta}$
where each transition $\tau \in \scrT$, is associated with a
transition relation of the form
\[
    \rho_{\tau}(\pVar,\pVar') \subseteq \setof{(\pVar,f_{\tau}(\pVar)) \;|\; g_\tau(\pVar) \land g'_\tau(f_{\tau}(\pVar))}
\]
where $f_{\tau}$ is an affine map relating the states and $g_{\tau}$,
$g'_{\tau}$ are affine guards (pre and post conditions) on the states.
The assertion on the initial states $\Theta$ is also affine.

We can now use a PWA transition system $\rho$ to approximate the
behavior of a hybrid dynamical system $\System$ defined by a simulator
$\simulate^{\System}$~\footnote{Due to $f_\tau$ being restricted to an affine
form, we can only approximate general hybrid systems.}. Each
transition of $\rho$ represents a discrete time step $\Delta$. Let the
state-space of $\System$ be given by $\x\in\HybridStates^n$, then the
states of $\rho$ are also given by $\x\in\HybridStates^n$. The affine guard
predicates $g_\tau$ are given by a conjunction of hyper-planes and
hence can be represented in matrix form as a polyhedron (defined by
$m$ constraints) in the state-space
\[
g:C\x - \vd \le 0
\]
where $C$ is an $m \times n$ matrix and $\vd$ is a vector of length
$m$. The affine maps $f_\tau$ can be represented in matrix form as
$f:\x \mapsto A\x+\vb$. To make $f_\tau$ `richer', we incorporate
an error term $\delta$ which is defined by a vector of intervals
$[\delta_{\min},\delta_{\max}]$. Hence,
\[
f:\x \mapsto A\x + \vb + \delta
\]
defines a set valued relation of the form $R:\setof{(\x,\x') \;|\; \x'
\in f_\tau(\x)}$.

@@

\begin{equation}
    \scrT = \left\{
        \begin{array}{ll}
            g_1(\x) \land g'_1(\x') \implies \x' \in f_1(\x) \\
            \ldots\\
            g_n(\x) \land g'_n(\x') \implies \x' \in f_n(\x) \\
        \end{array}
    \right.
\end{equation}

@@

where $f_i:\x \mapsto A_i\x + \vb_i + \delta_i$,
$g_i(\x):C_i\x-\vd_i\le0$, $g'_i(\x'):C'_i\x'-\vd'_i\le0$ and $\x'$
denotes the next state of the system.

@@

A PWA transition system is \textit{complete}, iff for every state
$\x\in\HybridStates^n$, there exists at least one satisfied
transition relation $\scrT$. If this is not the case, the system can
deadlock, with no further executions. This usually results from
incorrect modeling of SDCS, and from here on, we do not consider such
cases.

@@

\subsection{Learning Affine Function from Trajectory Segments}

The $\simulate$ function can be used to generate a data set of
relations parameterized by time $\Delta_t$, for different values of
states $\x_i$ and inputs $\vu_i$ as $\ds_{\Delta_t} =
\setof{(\x_i,\x'_i,\vu_i) | \x'_i = \simulate(\x_i,\vu_i)}$.
Moreover, by repeatedly applying $\simulate$, a discrete time series
of a finite length $N$ can be generated from a given state $\x_1$
and a sequence of inputs $\tupleof{\vu_1, \vu_2,\ldots,\vu_n}$ as shown
below.
\[\tupleof{\x_1, \x_2, \ldots, \x_n} \;\text{where}\; \x_{i>1} =
\simulate(\x_{i-1}, \vu_{i-1}, \Delta_t)\]

We now introduce a refinement of the data set $\ds \subseteq \ds$ by
incrementally observing the future states in the time series.

\[\ds_{\Delta_t} = \setof{(\x_i,\x'_i,\vu_i) | \x'_i =
\simulate(\x_i,\vu_i)}\]

\[\ds^{C_i} \subseteq \ds_t\]
\[\ds^{C_i}\]

$k$-Refinement of the data set $\ds^k$.
$\ds_k = \setof{(\x,\x',\vu) | \x' =  \simulate(\x,\vu,k\Delta_t)}$

state-input pairs of the form
$(\x,\x')$
data set equivalence traj segment
$D_c, $

>>>>

In this section, we present the model of the hybrid dynamical system
under test, and the background for pwa relational abstractions.

\mypara{The System under test $\System$} is assumed to be a hybrid
dynamical system. Its state is denoted by $\HybridStates \subseteq
\Modes \times \Reals^n$, where $\Modes$ is a finite set of discrete
modes. Let $\Inputs: [0,T] \rightarrow \reals^k$ be the set of input
signals to $\System$ over a finite time horizon $T$.

For the purpose of falsification, $\System$ is viewed as a black-box
equipped with a forward simulation map $\simulate^{\System}:
(\HybridStates, \vu, t) \mapsto \HybridStates$.  A simulation step
computes the unique reachable state $\vx \in \HybridStates$ in time
$t$ from a given state input pair $(\vx,\vu)$.  We formalize this
using the notion of time parameterized reachability relations
$\reach{t, \vu}_\System \subseteq \HybridStates \times \HybridStates$
detailed in~\cite{zutshi2014multiple}.
Hence, $\vy=\simulate^{\System}(\vx,u,t)$ \emph{iff} $\vx \reach{t,u}
\vy$.
% Given the hybrid state space $\vx\in\HybridStates$ and input space $u
% \in\Inputs$ and time step $t$, it computes the unique successor state
% $\vy=\simulate^{\System}(\vx,u,t)$ such that $\vx \reach{t,u} \vy$.

\myipara{System Assumptions:} We require that $\System$ be
forward deterministic. This
requires existence and uniqueness of trajectories over a finite time
horizon $[0,T]$, which can be guaranteed by Lipschitz continuity of
the vector field in each hybrid mode and ruling away issues such as
finite escape times~\cite{Meiss/2007/Differential}. From a practical
standpoint, these assumptions do not pose significant restrictions for
the type of problems that we wish to address. Finally, we assume full
observability of the system state, validate our results only against
the $\simulate$ function and {\em do not} assume that an analytic closed-form
representation of the system dynamics is available.

As the relations abstract the solution of a continuous time,
foward deterministic hybrid dynamical
system, they are deterministic, causal and satisfy the semi-group property.

From here on, we drop the subscript $\System$.

\begin{definition}
    The system under test $\System$ evolves in the set of infinite
    hybrid state-space $\HybridStates$ under the effect of inputs $\vu
    \in \Inputs$. Its evolution is defined by a simulation function
    $\simulate^\System : \HybridStates \times \Inputs \Reals^+ \mapsto
    \HybridStates$, where $\simulate^\System(\x,\vu,\Delta_t)$ maps a
    current state $\x$ at time $t$ to a new state $\x'$ at time
    $t+\Delta_t$, under a constant input $\vu$.
\end{definition}

@@

Best effor falsification works by enumerating the reachability
relations $\reach{}$ within a given budget. Depending upon the
specific instance of the problem, the budget can be prohibhitive,
requiring exponential computational and storage resources. Instead, we
proceed by summarizing these relations by their corresponding affine
maps using linear regression. The learnt analytical forms are
represented as $\vx' = A\vx + B\vu + \delta$, where $A$ and $B$ are
matrices and $\delta$ the estimated error.

@@

Let the data set be comprised of $N$ input and output pairs $(\x, y)$,
where $\x\in\reals^n$ and $y\in\reals$. If $N>n$, which is the case in
the current context of \textit{finding the best fit}, the problem is
over-determined: there are more equations than unknowns. Hence, a
single affine function cannot be found which satisfies the equation
$\forall i\in\{1\ldots N\}. y_i = \vec{a}^T\x_i + b$. Instead, we need
to find the `best' choice for $\vec{a}$ and $b$. This choice is formally
defined using a loss function. For the case of simple linear
regression or OLS, the loss function is the sum of squares of the
errors in prediction.  The task is then to determine the vector of
coefficients $\vec{a}$ and an offset constant $b$, such that the least
square error of the affine predictor is minimized for the given data
set.
\begin{equation}
    \operatornamewithlimits{argmin}_{\vec{a}, b}\displaystyle\sum_{i=1}^{N}{\left(\y_i - (\vec{a}^T\x_i + b)\right)^2}
\label{reg}
\end{equation}
To ease the presentation, we can rewrite the above as a homogeneous
expression by augmenting $\x$ by $\hat{\x} = \begin{bmatrix}\x \\ 1\end{bmatrix}$ and replacing $\vec{a}$ and $b$ by the vector
$\vec{ab} = \begin{bmatrix}\vec{a} \\ b \end{bmatrix}$. The equation~\ref{reg} now becomes
\[
    \operatornamewithlimits{argmin}_{\vec{ab}}\displaystyle\sum_{i=1}^{N}{(\y_i - \vec{ab}^T \hat{\x}_i)^2}
\]
The solution of OLS can be analytically computed as
\[ Ab = (X^TX)^{-1}X^T\y\]
where $X$ is the matrix representing the horizontal stacking of all
$\hat{\x}$.
The details can be found in standard texts on learning and statistics
\cite{friedman2001elements}.

@@

% \subsection{Relational Abstractions}
% For a hybrid automaton model, they can summarize the continuous
% dynamics of each mode using a binary relation over continuous states.
% The resulting relations are timeless (independent) and hence valid for
% all time as long as the mode invariant is satisfied. The relations
% take the general form of $R(\x,\x') \bowtie 0$, where $\bowtie$
% represents one of the relational operators $=, \ge, \le, <, >$. For
% example, an abstraction that captures the monotonicity with respect to
% time for the differential equation $\dot{x} = 2$ is $x' > x$. The
% abstraction capturing the relation between the set of ODEs: $\dot{x} =
% 2$, $\dot{y} = 5$, is $5(x' - x) = 2(y' - y)$.

@@

We define the PWA transition system as a transition system
%(ref.~\secref{DiscSys})
$\rho:\tupleof{\pLocs,\pVars,\scrT, \pLocI,\Theta}$
where each transition $\tau \in \scrT$, is associated with a
transition relation of the form
\[
    \rho_{\tau}(\pVar,\pVar') \subseteq \setof{(\pVar,\pVar')) \;|\;
    g_\tau(\pVar) \land g'_\tau(\pVar') \land f_{\tau}(\pVar, \pVar')}
\]
where $f_{\tau}$ is an affine relation on the pre and post states
$\pVar,\pVar'$, $g_{\tau}$ and $g'_{\tau}$ are affine guards (pre and
post conditions) on the states and $\Theta$ is an affine assertion on
the initial states.

We can now use a PWA transition system $\rho$ to approximate the
behavior of a hybrid dynamical system $\System$ defined by a simulator
$\simulate^{\System}$~\footnote{Due to $f_\tau$ being restricted to an affine
form, we can only approximate general hybrid systems.}. Each
transition of $\rho$ represents a discrete time step $\Delta$. Let the
state-space of $\System$ be given by $\x\in\HybridStates^n$, then the
states of $\rho$ are also given by $\x\in\HybridStates^n$. The affine guard
predicates $g_\tau$ are given by a conjunction of hyper-planes and
hence can be represented in matrix form as a polyhedron (defined by
$m$ constraints) in the state-space
\[
g:C\x - \vd \le 0
\]
where $C$ is an $m \times n$ matrix and $\vd$ is a vector of length
$m$. The affine relation $f_\tau$ can be represented using matrix $A$
and an offset vector $\vb$ as $f_\tau \subseteq \setof{(\x,\x') | \x'
= A\x+\vb}$. Finaly, we incorporte an approximate non-deterministic
error term $\delta$, defined as a vector of intervals
$[\delta_{\min},\delta_{\max}]$.
\[
    f_\tau \subseteq \setof{(\x,\x') | \x' = A\x+\vb}.
\]
%defines a set valued relation of the form $R:\setof{(\x,\x') \;|\; \x'
%\in f_\tau(\x)}$.

@@

\begin{equation}
    \scrT = \left\{
        \begin{array}{ll}
            g_1(\x) \land g'_1(\x') \implies f_1(\x,\x') \\
            \ldots\\
            g_n(\x) \land g'_n(\x') \implies f_n(\x,\x') \\
        \end{array}
    \right.
\end{equation}

@@

%where $f_i:\x \mapsto A_i\x + \vb_i + \delta_i$,
%$g_i(\x):C_i\x-\vd_i\le0$, $g'_i(\x'):C'_i\x'-\vd'_i\le0$ and $\x'$
where $g_i$ and $g'_i$ are affine predicates and $f_i$ are affine
relations and $\x'$ denotes the next state of the system.

@@

A PWA transition system is \textit{complete}, iff for every state
$\x\in\HybridStates^n$, there exists at least one satisfied
transition relation $\scrT$. If this is not the case, the system can
deadlock, with no further executions. This usually results from
modeling errors, and from here on, we do not consider such
cases.

@@

### 2017-04-07 pwarel.tex
.

We now briefly describe the approach. Given a numerical simulator
$\simulate$ and an initial abstraction defined by a quantization
function $\quant_\epsilon$ and a time step $\Delta$, we use
scatter-and-simulate (parameterized by number of samples $n$ as
described in \cite{zutshi2014multiple}) to explore the abstract graph
$\scr{H}(\Delta)$. The result is a graph $G$, which has a finite
number of abstract states $C$ (or cells) and edges $(C,C')$ iff $C
\areach{\Delta} C'$.

@@

@@

We now describe how relational models can be computed for a given
black box system by enriching the abstract reachability graph obtained
by scatter-and-simulate. We first formalize the notion of an enriched
graph, and then show how they can be interpreted as a PWA transition
system using $k$-relational modeling.

>>>>

\subsection{PWA Relational Abstraction}

Given an abstraction, we can define its enrichment

We now briefly overview the approach, which consists of three
steps

Discover the abstraction 
enriches the abstraction
formulates a BMC query
concretizes

abstraction defined by a quantization function $\quant_\epsilon$
time step $\Delta$

Given a numerical simulator
$\simulate$ and an initial abstraction defined by a quantization
function $\quant_\epsilon$ and a time step $\Delta$, we use
scatter-and-simulate (parameterized by number of samples $n$ as
described in \cite{zutshi2014multiple}) to explore the abstract graph
$\scr{H}(\Delta)$. The result is a graph $G$, which has a finite
number of abstract states $C$ (or cells) and edges $(C,C')$ iff $C
\areach{\Delta} C'$.

@@

\subsection{Graph Abstraction}
DEFINITION 3.4 (ABSTRACT STATE GRAPH). Let ∆ > 0 be
a fixed time step. The abstract state graph H(∆) for time step ∆
is defined by the set of vertices C, and edges (Ci, Cj ) whenever
Ci
∆ Cj . Let C0 denote the collection of initial cells in C, i.e., cells
Ci such that Ci ∩ X0 6= ∅. Further, let Cu denote the set of unsafe
cells, or cells Cj such that there is a state xj ∈ Cj that reaches
an unsafe state y ∈ Xf within time 0 ≤ tj < ∆. The abstraction
H(∆) is given by D
C,
∆ , C0, Cu
E
.

\subsection{Enriched Graph Abstraction}

@@

We now describe how relational models can be computed for a given
black box system by enriching the abstract reachability graph. We
first formalize the notion of an enriched graph, and then show how
they can be interpreted as a PWA transition system using
$k$-relational modeling.
